TacticToe: Learning to Prove with Tactics

### 2018-08-20 tactictoe_jv.tex
portability start
portability wip

>>>>

\paragraph{Portability}
Although \tactictoe is designed for \holfour, the ideas presented could be 
ported to another ITP. We highlight here the major modules of \tactictoe  some 
of the hurdles that developers might encounter during their re-implementation 
for another ITP:
\begin{itemize}
	\item A recording mechanism that can extract context-independent tactics 
	and the goal they were trying to solve. In our implementation, few tactics 
	are stateful and they usually become more powerful over time.
	\item Efficient tactics:
	\item Efficient predictors
	\item Efficient search: 
	 the MCTS algorithm should be re-implemented in the language of the 
	ITP, because better integration improves the efficiency of the algorithm.

\end{itemize}
